Live Functional Programming with Typed Holes

### 2018-10-26 intro.tex
replaced arxiv url in text with an arxiv citation + added cimini and siek 2016 citation to intro

\ifarxiv
The appendix 
\else
The extended version of the paper, which is included in the supplemental material and available from \url{https://arxiv.org/abs/1805.00155}, includes an appendix that 
\fi
(1) provides some straightforward auxiliary definitions and proofs that were omitted from the paper for the sake of space; and (2) defines some simple extensions to the core calculus (namely, numbers, and sum types), together with a brief exposition on defining further extensions. 
% These are not necessary to communicate the fundamental ideas of the paper, but may be of interest to some readers.

>>>>

\ifarxiv
The appendix 
\else
The extended version of the paper, which is included in the supplemental material and available online \cite{2018arXiv180500155O}, includes an appendix that 
\fi
(1) provides some straightforward auxiliary definitions and proofs that were omitted from the paper for the sake of space; and (2) defines some simple extensions to the core calculus (namely, numbers, and sum types), together with a brief discussion on  defining other extensions by following the approach of \citet{DBLP:conf/popl/CiminiS16}. 
% These are not necessary to communicate the fundamental ideas of the paper, but may be of interest to some readers.
